### 2023-03-29 source/intro.Rnw
typos and new references
fix data issue

\subsubsection{Example ``Reproducibility Project: Cancer Biology''}
I will now illustrate the assessment of replication success on data from the
``Reproducibility Project: Cancer Biology'' \citep{Errington2021}. This
large-scale project attempted to replicate 53 landmark studies from the field of
cancer biology \citep[and would perhaps better be named ``Replication Project'',
see][for the distinction between ``replicabality'' and
``reproducibility'']{Goodman2016}. In the end, only 23 of the 53 studies could
be repeated due to various difficulties, such as, missing information from the
original studies or problems in conducting the experiments.
\citet{Errington2021} report that these experiments led to data on 158
quantitative effects. However, from the data which they provide only 132
quantitative effects are provided with original and replication standardized
mean difference effect estimates along with standard errors, and only they will
be used in the subsequent analyses.

\begin{figure}[!htb]
<< "RPCB-graph", fig.height = 3.75 >>=
za <- qnorm(p = 0.975)
rpcb <- read.csv("data/rpcb.csv") |>
    mutate(id = paste0("(", paper, ", ", experiment, ", ", effect, ")"),
           zo = smdo/so,
           zr = smdr/sr,
           c = so^2/sr^2,
           d = smdr/smdo,
           po2 = 2*(1 - pnorm(q = abs(zo))),
           pr2 = 2*(1 - pnorm(q = abs(zr))),
           sm = 1/sqrt(1/so^2 + 1/sr^2),
           smdm = (smdo/so^2 + smdr/sr^2)*sm^2,
           pm2 = 2*(1 - pnorm(q = abs(smdm/sm))),
           Q = (smdo - smdr)^2/(so^2 + sr^2),
           pQ = pchisq(q = Q, df = 1, lower.tail = FALSE),
           rsig = factor(pr2 <= 0.05, levels = c(FALSE, TRUE),
                         labels = c("italic(p[r]) > 0.05",
                                    "italic(p[r]) <= 0.05")))
## compute sceptical p-value (TODO fix problems with NA)
ind <- !is.na(rpcb$zo) & !is.na(rpcb$zr) & !is.na(rpcb$c)
rpcb$ps1 <- NA
rpcb$ps1[ind] <- pSceptical(zo = rpcb$zo[ind], zr = rpcb$zr[ind], c = rpcb$c[ind],
                            alternative = "one.sided", type = "nominal")

zoom <- c(-2, 12)
alphazoom <- 0.6
ltyzoom <- 3
rpcbWithoutNA <- na.omit(rpcb)
cols <- adjustcolor(col = c("grey70", "grey5"), alpha.f = 0.8)
names(cols) <- levels(rpcbWithoutNA$rsig)
plotA <- ggplot(data = rpcbWithoutNA, aes(x = smdo, y = smdr)) +
    annotate(geom = "segment", x = zoom[1], xend = zoom[2],
             y = zoom[1], yend = zoom[1], alpha = alphazoom,
             lty = ltyzoom) +
    annotate(geom = "segment", x = zoom[1], xend = zoom[2],
             y = zoom[2], yend = zoom[2], alpha = alphazoom,
             lty = ltyzoom) +
    annotate(geom = "segment", x = zoom[1], xend = zoom[1],
             y = zoom[1], yend = zoom[2], alpha = alphazoom,
             lty = ltyzoom) +
    annotate(geom = "segment", x = zoom[2], xend = zoom[2],
             y = zoom[1], yend = zoom[2], alpha = alphazoom,
             lty = ltyzoom) +
    geom_abline(intercept = 0, slope = 1, alpha = 0.3) +
    geom_hline(yintercept = 0, lty = 2, alpha = 0.9, size = 0.4) +
    geom_vline(xintercept = 0, lty = 2, alpha = 0.9, size = 0.4) +
    geom_point(aes(fill = rsig), shape = 21) +
    geom_rug(aes(color = rsig), size = 0.3, show.legend = FALSE) +
    labs(x = "Original effect estimate (SMD)",
         y = "Replication effect estimate (SMD)",
         fill = "") +
    coord_fixed(xlim = c(-5, 30), ylim = c(-5, 30)) +
    scale_fill_manual(values = cols, labels = scales::parse_format()) +
    scale_color_manual(values = cols) +
    theme_bw() +
    theme(panel.grid = element_blank(),
          legend.position = c(0.5, 0.835))

plotB <- ggplot(data = rpcbWithoutNA, aes(x = smdo, y = smdr)) +
    geom_abline(intercept = 0, slope = 1, alpha = 0.3) +
    geom_hline(yintercept = 0, lty = 2, alpha = 0.9, size = 0.4) +
    geom_vline(xintercept = 0, lty = 2, alpha = 0.9, size = 0.4) +
    geom_point(aes(fill = rsig), shape = 21, show.legend = FALSE) +
    geom_rug(aes(color = rsig), size = 0.3, show.legend = FALSE) +
    labs(x = "Original effect estimate (SMD)",
         y = "Replication effect estimate (SMD)",
         fill = "") +
    coord_fixed(xlim = zoom, ylim = zoom) +
    scale_fill_manual(values = cols, labels = scales::parse_format()) +
    scale_color_manual(values = cols) +
    theme_bw() +
    theme(panel.grid = element_blank())
grid.arrange(plotA, plotB, ncol = 2)
@
\caption{Results for 132 effects from the ``Reproducibility Project: Cancer
  Biology'' \citep{Errington2021} for which effect estimates and standard errors
  are available on standardized mean difference (SMD) scale. The right plot
  shows a zoomed-in view of the dotted area in the left plot. The
  \textit{p}-values are recomputed using a normal approximation. Two study pairs
  with original effect estimate larger than 80 are not shown.}
\label{fig:rpcb}
\end{figure}

@@

Figure~\ref{fig:upset} shows how many of the replications are successful
according to the criteria from Table~\ref{tab:rsdef} (except the confidence
interval criteria since they do not take into account the uncertainty from both
studies). For the total 132 replications, most successes occur for the
meta-analytic significance (\Sexpr{nma}) and the prediction interval criteria
(\Sexpr{npi}), followed by significance (\Sexpr{nsig}), and relative effect size
(\Sexpr{nres}). However, looking at the combinations of the criteria, only in
two replications are all criteria satisfied simultaneously (green).

A detailed view for a subset of the data from the project is given in
Table~\ref{tab:RPCB}. The subset is randomly chosen such that from every
original study one effect and one replication of that effect is included. For
the three replications at the bottom of the table (\#18, \#19, and \#20), all
criteria indicate replication failure. For the other replications, the
conclusions are more ambiguous as in no single case are all criteria met
simultaneously. For instance, the first three replications satisfy the
significance criterion ($p_{o} < 0.05$ and $p_{r} < 0.05$), the meta analytic
significance criterion ($p_{m} < 0.05$) and the $Q$-test/prediction interval
criterion ($p_{Q} > 0.05$), yet the replication effect estimate is smaller than
the original one so does not satisfy the relative effect size criterion
($d < 1$). The fourth replication, on the other hand, satisfies the relative
effect size criterion ($d \geq 1$) but fails to satisfy the significance
criterion as the original study was not significant ($p_{o} > 0.05$).
% For example, replication \#17 is a clear
% failure with respect to the relative effect estimate ($d < 1$) and the
% significance criteria ($p_{o} > 0.05$ and $p_{r} > 0.05$), yet the $Q$-test does
% not indicate evidence for inconsistency of the two effect estimates
% ($p_{Q} > 0.05$).

@@

## randomly select a subset with one effect per paper
set.seed(7)
rpcbTable <- rpcb |>
    na.omit() |>
    group_by(paper) |>
    sample_n(size = 1) |>
    ungroup() |>
    arrange(ps1) |>
    mutate(smdoFormat = signif(smdo, 3),
           smdrFormat = signif(smdr, 3),
           smdmFormat = signif(smdm, 3),
           dFormat = tableFormat(x = d, outFun = dFormat,
                                 threshold = 1, col1 = "dark2orange", font1 = "mathrm",
                                  col2 = "dark2green", font2 = "mathbf"),
           cioL = smdo - za*so,
           cioU = smdo + za*so,
           cirL = smdr - za*sr,
           cirU = smdr + za*sr,
           cimL = smdm - za*sm,
           cimU = smdm + za*sm,,
           po2Format = tableFormat(x = po2),
           pr2Format = tableFormat(x = pr2),
           pm2Format = tableFormat(x = pm2),
           ps1Format = tableFormat(x = ps1, threshold = 0.025),
           pQFormat = tableFormat(x = pQ, col1 = "dark2orange", font1 = "mathrm",
                                  col2 = "dark2green", font2 = "mathbf"),
           cioFormat = ciFormat(lower = cioL, upper = cioU, dollar = TRUE),
           cirFormat = ciFormat(lower = cirL, upper = cirU, dollar = TRUE),
           cimFormat = ciFormat(lower = cimL, upper = cimU), dollar = TRUE) |>
    select(id,
           smdoFormat, cioFormat,
           smdrFormat, cirFormat,
           smdmFormat, cimFormat,
           c, dFormat,
           po2Format, pr2Format, pm2Format, pQFormat, ps1Format
           )
rpcbXtable <- xtable(rpcbTable)
colnames(rpcbXtable) <- c("(P, X, E)",
                          "$\\that_o$", "(95\\% CI)",
                          "$\\that_r$", "(95\\% CI)",
                          "$\\that_m$", "(95\\% CI)",
                          "$c$",
                          "$d$",
                          "$p_o$",
                          "$p_r$",
                          "$p_m$",
                          "$p_Q$",
                          "$p_{\\text{S}}$"
                          )

@@

zr <- tr/sr
c <- so^2/sr^2
ps <- pSceptical(zo = zo, zr = zr, c = c, alternative = "two.sided", type = "nominal")
psFormat <- pFormat(p = ps)
@
\subsubsection{The sceptical \textit{p}-value}
To remove the dependence on the level $\alpha$, \citet{Held2020} proposed to
determine the smallest level at which replication success can be established.
This level is called the \emph{sceptical $p$-value} $p_{\text{S}}$, and it is
available in closed-form
\begin{align}
  \label{eq:ps}
  p_{\text{S}}
  % = \inf_{\alpha \in (0, 1)} \left\{\alpha : p_{\text{Box}} \leq \alpha \right\}.
  = 2\left\{1 - \Phi(|z_{\text{S}}|)\right\}
\end{align}
where
\begin{align*}
  z_{\text{S}}^{2}
  = \begin{cases}
    z^{2}_{\text{H}}/2 & \text{for} ~ c = 1 \\
    \left\{\left[z_{\text{A}}^{2}\left\{z_{\text{A}}^{2} +
          z_{\text{H}}^{2}(c - 1)\right\}\right]^{1/2}
      - z_{\text{A}}^{2}\right\}/(c - 1)
    & \text{for} ~ c \neq 1
  \end{cases}
\end{align*}
with arithmetic mean $z_{\text{A}}^{2} = (z^{2}_{o} + z^{2}_{r})/2$ and harmonic
mean $z_{\text{H}}^{2} = 2/(1/z^{2}_{o} + 1/z^{2}_{r})$ of the squared
$z$-statistics, and variance ratio $c = \sigma^{2}_{o}/\sigma^{2}_{r}$. A
sceptical $p$-value $\ps \leq \alpha$ is then equivalent to replication success
at level $\alpha$. For instance, the sceptical $p$-values of the three
replication studies in Figure~\ref{fig:RBillustration} are
$p_{\text{S}} = \Sexpr{psFormat[1]}$, $p_{\text{S}} = \Sexpr{psFormat[2]}$, and
$p_{\text{S}} = \Sexpr{psFormat[3]}$ (from left to right), so we can see that
the third replication is unsuccessful at level $\alpha = 5\%$ but successful at
level $\alpha = 10\%$. However, the sceptical $p$-value does not necessarily
have to be dichotomized in this manner, but can also be interpreted as a
quantitative measure of replication success; the smaller $p_{\text{S}}$, the
higher the degree of replication success.

@@

The last column of Table~\ref{tab:RPCB} shows the one-sided sceptical $p$-value
for the subset of replications from the ``Reproducibility Project: Cancer
Biology''. The results illustrate the previously discussed properties to require
significance from both studies and to penalize effect shrinkage. For example,
replication \#4 fails to achieve replication success at level $\alpha = 2.5\%$
with the one-sided sceptical $p$-value, even though the replication study was
highly convincing (the effect estimate was almost five times as large as in the
original study). Yet, as the approach requires both studies to be convincing on
their own -- and the original study was not significant at the 2.5\% level
(one-sided) -- replication success at this level is impossible with the
sceptical $p$-value. The second property is illustrated by replication \#8. Here
both the original and replication studies were significance. However, the effect
estimate from the replication was roughly 60\% smaller than the one from the
original study, and significance is merely achieved because the standard error
was much smaller (\ie{} around $1/\surd c \approx 1/2.8$ times smaller). The
sceptical $p$-value is therefore only $p_{\text{S}} = 0.12$, indicating less
evidence for replication success.

@@

\startPaperSummary{PaperVI}{%
  Pitfalls and Potentials in Simulation Studies}{%
  Samuel Pawel, Lucas Kook, Kelly Reeve \\
  \textit{Biometrical Journal}, 2023.
  doi:\href{https://doi.org/10.1002/bimj.202200091}{10.1002/bimj.202200091}.}

@@

\phantomsection
\addcontentsline{toc}{section}{Data and software}
\section*{Data and software}
The CC-By 4.0 licensed data from the ``Reproducibility Project: Cancer Biology''
\citep{Errington2021} were downloaded from
\url{https://doi.org/10.17605/osf.io/e5nvr}. The relevant variables were then
extracted from the file ``\texttt{RP\_CB Final Analysis - Effect level
  data.csv}''. All analyses from this chapter were conducted in the R
programming language version \Sexpr{paste(version$major, version$minor, sep =
  ".")} \citep{R}. The packages \texttt{dplyr} \citep{Wickham2022},
\texttt{ggplot2} \citep{Wickham2016}, \texttt{gridExtra} \citep{Auguie2017},
\texttt{knitr} \citep{Xie2022}, \texttt{ReplicationSuccess} \citep{Held2020},
\texttt{scales} \citep{Wickham2022b}, \texttt{UpSetR} \citep{Gehlenborg2019},
and \texttt{xtable} \citep{Dahl2019} were used. Code and data to reproduce this
thesis are available at \url{https://github.com/SamCH93/thesis}. A snapshot of
the git repository is archived at \url{https://doi.org/10.5281/zenodo.7464296}.

>>>>

<< "RPCB-data" >>=
rpcb <- read.csv("data/rpcb-outcome-level.csv") |>
    mutate(id = paste0("(", paper, ", ", experiment, ", ", effect, ")"),
           zo = smdo/so,
           zr = smdr/sr,
           c = so^2/sr^2,
           d = smdr/smdo,
           po2 = 2*(1 - pnorm(q = abs(zo))),
           pr2 = 2*(1 - pnorm(q = abs(zr))),
           sm = 1/sqrt(1/so^2 + 1/sr^2),
           smdm = (smdo/so^2 + smdr/sr^2)*sm^2,
           pm2 = 2*(1 - pnorm(q = abs(smdm/sm))),
           Q = (smdo - smdr)^2/(so^2 + sr^2),
           pQ = pchisq(q = Q, df = 1, lower.tail = FALSE),
           rsig = factor(pr2 <= 0.05, levels = c(FALSE, TRUE),
                         labels = c("italic(p[r]) > 0.05",
                                    "italic(p[r]) <= 0.05"))## ,
           ## rsig = factor(pr <= 0.05, levels = c(FALSE, TRUE),
           ##               labels = c("italic(p[r]) > 0.05",
           ##                          "italic(p[r]) <= 0.05"))
           ## ## uncomment for the same significance assessment as in RPCB paper
           ## ## (differs in some cases due to normal approximation)
           )
## compute sceptical p-value (TODO fix problems with NA)
ind <- !is.na(rpcb$zo) & !is.na(rpcb$zr) & !is.na(rpcb$c)
rpcb$ps1 <- NA
rpcb$ps1[ind] <- pSceptical(zo = rpcb$zo[ind], zr = rpcb$zr[ind], c = rpcb$c[ind],
                            alternative = "one.sided", type = "nominal")
rpcbWithoutNA <- na.omit(rpcb)
@

\subsubsection{Example ``Reproducibility Project: Cancer Biology''}
I will now illustrate the assessment of replication success on data from the
``Reproducibility Project: Cancer Biology'' \citep{Errington2021}. This
large-scale project attempted to replicate 53 landmark studies from the field of
cancer biology \citep[and would perhaps better be named ``Replication Project'',
see][for the distinction between ``replicability'' and
``reproducibility'']{Goodman2016}. In the end, only 23 of the 53 studies could
be repeated due to various difficulties, such as, missing information from the
original studies or problems in conducting the experiments.
\citet{Errington2021} report that these experiments led to data on 158
quantitative effects. However, from the data which they provide only
\Sexpr{nrow(rpcb)} quantitative effects are provided with original and
replication standardized mean difference effect estimates along with standard
errors, and only they will be used in the subsequent analyses.

\begin{figure}[!htb]
<< "RPCB-graph", fig.height = 3.75 >>=
za <- qnorm(p = 0.975)
zoom <- c(-2, 12) # c(-2.5, 5) # in original plot
alphazoom <- 0.6
ltyzoom <- 3
cols <- adjustcolor(col = c("grey70", "grey5"), alpha.f = 0.8)
names(cols) <- levels(rpcbWithoutNA$rsig)
plotA <- ggplot(data = rpcbWithoutNA, aes(x = smdo, y = smdr)) +
    annotate(geom = "segment", x = zoom[1], xend = zoom[2],
             y = zoom[1], yend = zoom[1], alpha = alphazoom,
             lty = ltyzoom) +
    annotate(geom = "segment", x = zoom[1], xend = zoom[2],
             y = zoom[2], yend = zoom[2], alpha = alphazoom,
             lty = ltyzoom) +
    annotate(geom = "segment", x = zoom[1], xend = zoom[1],
             y = zoom[1], yend = zoom[2], alpha = alphazoom,
             lty = ltyzoom) +
    annotate(geom = "segment", x = zoom[2], xend = zoom[2],
             y = zoom[1], yend = zoom[2], alpha = alphazoom,
             lty = ltyzoom) +
    geom_abline(intercept = 0, slope = 1, alpha = 0.3) +
    geom_hline(yintercept = 0, lty = 2, alpha = 0.9, size = 0.4) +
    geom_vline(xintercept = 0, lty = 2, alpha = 0.9, size = 0.4) +
    geom_point(aes(fill = rsig), shape = 21) +
    geom_rug(aes(color = rsig), size = 0.3, show.legend = FALSE) +
    labs(x = "Original effect estimate (SMD)",
         y = "Replication effect estimate (SMD)",
         fill = "") +
    coord_fixed(xlim = c(-5, 30), ylim = c(-5, 30)) +
    scale_fill_discrete(labels = scales::parse_format()) +
    ## scale_fill_manual(values = cols, labels = scales::parse_format()) +
    ## scale_color_manual(values = cols) +
    theme_bw() +
    theme(panel.grid = element_blank(),
          legend.position = c(0.5, 0.835))

plotB <- ggplot(data = rpcbWithoutNA, aes(x = smdo, y = smdr)) +
    geom_abline(intercept = 0, slope = 1, alpha = 0.3) +
    geom_hline(yintercept = 0, lty = 2, alpha = 0.9, size = 0.4) +
    geom_vline(xintercept = 0, lty = 2, alpha = 0.9, size = 0.4) +
    geom_point(aes(fill = rsig), shape = 21, show.legend = FALSE) +
    geom_rug(aes(color = rsig), size = 0.3, show.legend = FALSE) +
    labs(x = "Original effect estimate (SMD)",
         y = "Replication effect estimate (SMD)",
         fill = "") +
    coord_fixed(xlim = zoom, ylim = zoom) +
    ## scale_fill_manual(values = cols, labels = scales::parse_format()) +
    ## scale_color_manual(values = cols) +
    theme_bw() +
    theme(panel.grid = element_blank())
grid.arrange(plotA, plotB, ncol = 2)
## cf Figure 2—figure supplement 1
## https://iiif.elifesciences.org/lax/71601%2Felife-71601-fig2-figsupp1-v3.tif/full/1500,/0/default.jpg
@
\caption{Results from \Sexpr{nrow(rpcb)} replication studies from the
  ``Reproducibility Project: Cancer Biology'' \citep{Errington2021} for which
  effect estimates and standard errors are available on standardized mean
  difference (SMD) scale. The right plot shows a zoomed-in view of the dotted
  area in the left plot. The \textit{p}-values are recomputed using a normal
  approximation. Two study pairs with original effect estimate larger than 80
  are not shown.}
\label{fig:rpcb}
\end{figure}

@@

Figure~\ref{fig:upset} shows how many of the replications are successful
according to the criteria from Table~\ref{tab:rsdef} (except the confidence
interval criteria since they do not take into account the uncertainty from both
studies). For the total \Sexpr{nrow(rpcb)} replications, most successes occur
for the meta-analytic significance (\Sexpr{nma}) and the prediction interval
criteria (\Sexpr{npi}), followed by significance (\Sexpr{nsig}), and relative
effect size (\Sexpr{nres}). However, looking at the combinations of the
criteria, only in two replications are all criteria satisfied simultaneously
(green).

A detailed view for an illustrative subset of the data from the project is given
in Table~\ref{tab:RPCB}. The subset is chosen such that from every original
study one effect and one replication of that effect is included. For two
replications at the bottom of the table (\#18 and \#20), all criteria indicate
replication failure. For the other replications, the conclusions are more
ambiguous as in no single case are all criteria met simultaneously. For
instance, the first three replications satisfy the significance criterion
($p_{o} < 0.05$ and $p_{r} < 0.05$), the meta analytic significance criterion
($p_{m} < 0.05$) and the $Q$-test/prediction interval criterion
($p_{Q} > 0.05$), yet the replication effect estimate is smaller than the
original one so does not satisfy the relative effect size criterion ($d < 1$).
The fourth replication, on the other hand, satisfies the relative effect size
criterion ($d \geq 1$) but fails to satisfy the significance criterion for the
original study ($p_{o} > 0.05$) and the $Q$-test/prediction interval criterion
($p_{Q} \leq 5\%$).

@@

## randomly select a subset with one effect per paper
set.seed(7)
rpcbTable1 <- rpcb |>
    na.omit() |>
    group_by(paper) |>
    sample_n(size = 1) |>
    ungroup() |>
    arrange(ps1) |>
    mutate(smdoFormat = signif(smdo, 3),
           smdrFormat = signif(smdr, 3),
           smdmFormat = signif(smdm, 3),
           dFormat = tableFormat(x = d, outFun = dFormat,
                                 threshold = 1, col1 = "dark2orange", font1 = "mathrm",
                                  col2 = "dark2green", font2 = "mathbf"),
           cioL = smdo - za*so,
           cioU = smdo + za*so,
           cirL = smdr - za*sr,
           cirU = smdr + za*sr,
           cimL = smdm - za*sm,
           cimU = smdm + za*sm,,
           po2Format = tableFormat(x = po2),
           pr2Format = tableFormat(x = pr2),
           pm2Format = tableFormat(x = pm2),
           ps1Format = tableFormat(x = ps1, threshold = 0.025),
           pQFormat = tableFormat(x = pQ, col1 = "dark2orange", font1 = "mathrm",
                                  col2 = "dark2green", font2 = "mathbf"),
           cioFormat = ciFormat(lower = cioL, upper = cioU, dollar = TRUE),
           cirFormat = ciFormat(lower = cirL, upper = cirU, dollar = TRUE),
           cimFormat = ciFormat(lower = cimL, upper = cimU), dollar = TRUE)
rpcbTable <- rpcbTable1 |>
    select(id,
           smdoFormat, cioFormat,
           smdrFormat, cirFormat,
           smdmFormat, cimFormat,
           c, dFormat,
           po2Format, pr2Format, pm2Format, pQFormat, ps1Format
           )
rpcbXtable <- xtable(rpcbTable)
colnames(rpcbXtable) <- c("(P, X, E)",
                          "$\\that_o$", "(95\\% CI)",
                          "$\\that_r$", "(95\\% CI)",
                          "$\\that_m$", "(95\\% CI)",
                          "$c$",
                          "$d$",
                          "$p_o$",
                          "$p_r$",
                          "$p_m$",
                          "$p_Q$",
                          "$p_{\\text{S}}$"
                          )

@@

zr <- tr/sr
c <- so^2/sr^2
ps <- pSceptical(zo = zo, zr = zr, c = c, alternative = "two.sided", type = "nominal")
psFormat <- pFormat(p = ps)
@

\subsubsection{The sceptical \textit{p}-value}
To remove the dependence on the level $\alpha$, \citet{Held2020} proposed to
determine the smallest level at which replication success can be established.
This level is called the \emph{sceptical $p$-value} $p_{\text{S}}$, and it is
available in closed-form
\begin{align}
  \label{eq:ps}
  p_{\text{S}}
  % = \inf_{\alpha \in (0, 1)} \left\{\alpha : p_{\text{Box}} \leq \alpha \right\}.
  = 2\left\{1 - \Phi(|z_{\text{S}}|)\right\}
\end{align}
where
\begin{align*}
  z_{\text{S}}^{2}
  = \begin{cases}
    z^{2}_{\text{H}}/2 & \text{for} ~ c = 1 \\
    \left\{\left[z_{\text{A}}^{2}\left\{z_{\text{A}}^{2} +
          z_{\text{H}}^{2}(c - 1)\right\}\right]^{1/2}
      - z_{\text{A}}^{2}\right\}/(c - 1)
    & \text{for} ~ c \neq 1
  \end{cases}
\end{align*}
with arithmetic mean $z_{\text{A}}^{2} = (z^{2}_{o} + z^{2}_{r})/2$ and harmonic
mean $z_{\text{H}}^{2} = 2/(1/z^{2}_{o} + 1/z^{2}_{r})$ of the squared
$z$-statistics, and variance ratio $c = \sigma^{2}_{o}/\sigma^{2}_{r}$. A
sceptical $p$-value $\ps \leq \alpha$ is then equivalent to replication success
at level $\alpha$. For instance, the sceptical $p$-values of the three
replication studies in Figure~\ref{fig:RBillustration} are
$p_{\text{S}} = \Sexpr{psFormat[1]}$, $p_{\text{S}} = \Sexpr{psFormat[2]}$, and
$p_{\text{S}} = \Sexpr{psFormat[3]}$ (from left to right), so we can see that
the third replication is unsuccessful at level $\alpha = 5\%$ but successful at
level $\alpha = 10\%$. However, the sceptical $p$-value does not necessarily
have to be dichotomized in this manner, but can also be interpreted as a
quantitative measure of replication success; the smaller $p_{\text{S}}$, the
higher the degree of replication success.

@@

<< "examples-sceptical-p" >>=
ex2 <- rpcbTable1[5,]
@

The last column of Table~\ref{tab:RPCB} shows the one-sided sceptical $p$-value
for the subset of replications from the ``Reproducibility Project: Cancer
Biology''. The results illustrate the previously discussed properties to require
significance from both studies and to penalize effect shrinkage. For example,
replication \#4 fails to achieve replication success at level $\alpha = 2.5\%$
with the one-sided sceptical $p$-value, even though the replication study was
highly convincing (the effect estimate was almost five times as large as in the
original study). Yet, as the approach requires both studies to be convincing on
their own -- and the original study was not significant at the 2.5\% level
(one-sided) -- replication success at this level is impossible with the
sceptical $p$-value. The second property is illustrated by replication \#5. Here
both the original and replication studies were significance. However, the effect
estimate from the replication was roughly \Sexpr{round(100*(1 - ex2$d), 0)}\%
smaller than the one from the
original study, and significance is merely achieved because the standard error
was much smaller (\ie{} around
$1/\surd c \approx 1/\Sexpr{round(sqrt(ex2$c), 2)}$ times smaller). The
sceptical $p$-value is therefore only
$p_{\text{S}} = \Sexpr{pFormat(ex2[,"ps1"])}$, indicating less evidence for
replication success.

@@

\startPaperSummary{PaperVI}{%
  Pitfalls and Potentials in Simulation Studies}{%
  Samuel Pawel, Lucas Kook, Kelly Reeve \\
  \textit{Biometrical Journal}, 2023, e2200091.
  doi:\href{https://doi.org/10.1002/bimj.202200091}{10.1002/bimj.202200091}.}

@@

\phantomsection
\addcontentsline{toc}{section}{Data and software}
\section*{Data and software}
The CC-By 4.0 licensed data from the ``Reproducibility Project: Cancer Biology''
\citep{Errington2021} were downloaded from
\url{https://github.com/mayamathur/rpcb} (commit a1e0c63). The R script
\texttt{preprocess-rpcb-data.R} available on the git repository accompanying
this thesis shows all preproccessing steps that were performed for extracting
the relevant variables. All analyses from this chapter were conducted in the R
programming language version \Sexpr{paste(version$major, version$minor, sep =
  ".")} \citep{R}. The packages \texttt{dplyr} \citep{Wickham2022},
\texttt{ggplot2} \citep{Wickham2016}, \texttt{gridExtra} \citep{Auguie2017},
\texttt{knitr} \citep{Xie2022}, \texttt{ReplicationSuccess} \citep{Held2020},
\texttt{scales} \citep{Wickham2022b}, \texttt{UpSetR} \citep{Gehlenborg2019},
and \texttt{xtable} \citep{Dahl2019} were used. Code and data to reproduce this
thesis are available at \url{https://github.com/SamCH93/thesis}. A snapshot of
the git repository is archived at \url{https://doi.org/10.5281/zenodo.7464296}.
